### 2024-08-04 conteudo/background/refactor.tex
add refactor methods

\subsection{Parameterize method}

TODO. I EXPECT TO FILL THIS SECTION AS THE WORK EVOLVES.

>>>>

\paragraph{Parameterize method}

\

The Parameterize method consists of replacing multiple similar codes with a singular function. 
The function created implements the different behaviors between similar codes by using parameters, 
which tell which behavior the function should use \citep{refactorbook}.
Figure (CREATE FIGURE AND ADD HERE) demonstrates an example of the Parameterize method usage.

\paragraph{Extract method}

\

The Extract method consists of splitting a complex code artifact into multiple simple methods/functions. 
One of the advantages of this method is enabling the created functions to be used multiple times through 
the code project. In contrast, with only the complex code artifact, it is not always possible to reuse 
it entirely, thus creating a new code duplication \citep{refactorbook}. 
Figure (CREATE FIGURE AND ADD HERE) demonstrates an example of the Extract method usage.
